---
title: "p8105_hw1_ts3593"
author: "Shi Tiancheng"
date: "2024-09-21"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("palmerpenguins")
```
Problem 1
```{r}
library(ggplot2)
```

```{r}
data("penguins", package = "palmerpenguins")
```

```{r}
summary(penguins)
```
There are 8 variables in the dataset.
They are species(Adelie, Chinstrap, Gentoo), island(Biscoe, Dream, Torgersen), bill_length_mm(32.1 to 59.6), bill_depth_mm(13.1 to 21.5), flipper_length_mm(172 to 231), body_mass_g(2700 to 6300), sex(female, male), year(2007 to 2009).
There are total 344 observations.


```{r}
nrow(penguins)
ncol(penguins)
```
There are 8 variables and 344 columns.
The mean of the flipper length is 200.9.
```{r}
plot<-ggplot(penguins,aes(x=bill_length_mm,y=flipper_length_mm,color=species),color=species)+geom_point()
plot
```

```{r}
ggsave(plot,
       filename = "scatterplot.jpg",
       width = 7,
       height = 5.5)
```

Problem2
```{r}
library(tidyverse)
```

```{r}
data_2 = tibble(
  sample = rnorm(10),
  vec_logical = c(sample > 0),
  vec_char10 = c("a","b","c","d","e","f","g","h","i","j"),
  vec_factor = factor(c(sample(1:3,10, replace = T)))
)
data_2
```

```{r}
mean(pull(data_2, var = sample))
```
```{r}
mean(pull(data_2, var = vec_logical))
```
```{r}
mean(pull(data_2, var = vec_factor))
```

```{r}
mean(pull(data_2, var = vec_char10))
```
sample and vec_logical can get mean. 
vec_char10 and vec_factor cannot get mean.

```{r}
mean(as.numeric(pull(data_2, var = vec_factor)))
mean(as.numeric(pull(data_2, var = vec_char10)))
```
After applying as.numeric, var_factor can take the mean.
Because char cannot convert to numeric. 

